N-dimensional Tic Tac Toe, and Adventure in Modules

### 2017-05-12 paper/paper.tex

	\section{Design Decisions}
  % (Most important!) Describe in detail 3-5 design decisions you made during your
  % project, with respect to abstraction and/or modularity. For example, what is a
  % piece of information that you chose to hide and why? How did you decide on a
  % particular way of separating your system into modules compared to another. How
  % did you reduce coupling between two modules? These design decisions should
  % emphasize how you applied ideas from the papers we’ve read (and associated
  % discussions) to the design of your project. It might be helpful here to
  % include snippets from old versions (or hypothetical alternative versions) of
  % your project to compare and contrast with the final version.
  \subsection{Creating an Abstract Game Engine}
  % How we came up with the abstract design
  \subsection{Exploiting Structural Typing}
  % Something about how previously we just had signature -> structure -> functors
  % but with include it became possible to
  One major element of SML's module system that we were about to exploit in our project was
  the structural matching of modules to signatures. Coupled with liberal use of the \texttt{include}
  keyword, this allowed us to easily extend signature definitions in a way reminiscent of inheritance
  and subclassing in OOP.

>>>>

	\section{Design Decisions}
  % (Most important!) Describe in detail 3-5 design decisions you made during your
  % project, with respect to abstraction and/or modularity. For example, what is a
  % piece of information that you chose to hide and why? How did you decide on a
  % particular way of separating your system into modules compared to another. How
  % did you reduce coupling between two modules? These design decisions should
  % emphasize how you applied ideas from the papers we’ve read (and associated
  % discussions) to the design of your project. It might be helpful here to
  % include snippets from old versions (or hypothetical alternative versions) of
  % your project to compare and contrast with the final version.

  \subsection{Creating an Abstract Game Engine}
  % How we came up with the abstract design
  The design for our game engine stemmed from trying to isolate the common
  general components of what would be required to create a running game.
  Rather than focus on creating one specific game implementation where these
  problems are addressed in an \textit{ad hoc} way, we wanted to
  look at the larger picture and view the problem in terms of the common pattern
  that emerged between these kinds of games.

  Each of the portions of the \textit{State}-\textit{Actions}-\textit{Agents}
  design is independent so that - once created - it does not rely on other
  modules for its internal pieces.
  Each of the constituent parts of the game engine is more akin to a node on a
  graph and the interfaces are like edges.
  The pieces should be thought of as islands of code that could then interact
  with other modules. By using the game model to define a specific game - we
  essentially create more specific versions of those islands following the
  recipe spelled out in the signatures.

\subsection{Exploiting Structural Typing}
  % Something about how previously we just had signature -> structure -> functors
  % but with include it became possible to
  One major element of SML's module system that we were about to exploit in our project was
  the structural matching of modules to signatures. Coupled with liberal use of the \texttt{include}
  keyword, this allowed us to easily extend signature definitions in a way reminiscent of inheritance
  and subclassing in OOP.
